---
title: "R Notebook"
output: html_notebook
---

###------Libraries-----####
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(stringr)
library(data.table)
library(ggplot2)
library(RColorBrewer)
```

###------ Loading in the scraped data  -----####
```{r}
setwd('/Users/carolinetvergaard/Desktop/NLP/scraping/new')
files <- list.files(path = "/Users/carolinetvergaard/Desktop/NLP/scraping/new", pattern = "*.csv", full.names = T)
tblnew <- sapply(files, read_csv, simplify=FALSE) %>% 
  bind_rows()

tblnew <- tblnew[!(tblnew$Description=="None"),]
tblnew <- tblnew %>% distinct()
```

###------ Import dataset after gender bias analysis in python notebook -----####
```{r}
df_tags <- read_csv("df_tags27dec.csv")
df_salary <- read_csv("df_salary27dec.csv")
df_seek_30 <- read_csv("Desktop/NLP/scraping/NEW_df_seek_30.csv")
```

###------ Fixing mistakes -----####
just FYI der has been much more 'cleaning' and 'playing around' that you have been spared in this script :-) 
```{r}
indeed_occupation <- df_tags
indeed_occupation$Sector[indeed_occupation$Sector == "Business & Finance"  | indeed_occupation$Sector == "Busuiness, Consulting & Management"] <- "Business, Consulting & Management"
indeed_occupation$Sector[indeed_occupation$Occupation == "Pharmacist"] <- "Healthcare & Social Assistance"


unique(indeed_occupation$Sector)

DT <- indeed_occupation
DT <- dplyr::filter(DT,  !is.na(Sector))
indeed_occupation <- DT

list <- list(unique(DT$Occupation))

new_seek <- df_seek_30
new_seek <- new_seek[!(new_seek$job_description=="nan"),]
```

###------ saving cleaned datasets -----####
```{r}
write_csv(new_seek, "DF_SEEK_CLEAN_BIAS.csv")
write_csv(df_bias, "DF_INDEED_CLEAN_BIAS.csv")
```

###------ Density plots -----####
```{r}
ggplot(data=df_bias, aes(df_bias$man_woman)) + 
  geom_histogram(aes(y =..density..),col="red", fill="green", alpha=.2) + 
  geom_density(col=2)

ggplot(data=new_seek, aes(new_seek$man_woman)) + 
  geom_histogram(aes(y =..density..),col="red", fill="green", alpha=.2) + 
  geom_density(col=2)
```

###------ Linear Regression Models -----####
```{r}
lm_occu <- lm(man_woman ~ Occupation, df_bias)
summary(lm_occu)
lm_occu <- lm(man_woman ~ Sector, df_bias)
summary(lm_occu)
lm_sec_30 <- lm(man_woman ~ category, df_seek_30)
summary(lm_sec_30)
```

###------ Plots - Gender bias per occupation -----####
```{r}
ggplot(df_bias, aes(x= reorder(Occupation, -father_mother), y=father_mother, label=father_mother, fill=Sector)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  scale_fill_manual(breaks = c("Construction", "Transport, Postal and Warehousing", "Manufacturing", "Professional, Scientific and Technical Services", "Business, Consulting & Management", "Accommodation & Food Services", "Retail Trade", "Creative Arts & Design",  "Education & Training", "Healthcare & Social Assistance"), 
                       values=c("blue4", "blue3", "blue2", "blueviolet", "blue1", "cadetblue3", "chocolate", "coral3" ,"coral1" ,"brown1"))
```

###------ Plots - Gender bias Indeed per Sector -----####
```{r}
ggplot(df_bias, aes(x= reorder(Sector, -man_woman), y=man_woman, label=man_woman, fill=Sector)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  scale_fill_manual(breaks = c("Construction", "Transport, Postal and Warehousing", "Manufacturing", "Professional, Scientific and Technical Services", "Business, Consulting & Management", "Accommodation & Food Services", "Retail Trade", "Creative Arts & Design",  "Education & Training", "Healthcare & Social Assistance"), 
                       values=c("blue4", "blue3", "blue2", "blueviolet", "blue1", "cadetblue3", "chocolate", "coral3" ,"coral1" ,"brown1"))
```
###------ Plots - Gender bias SEEK per Sector/category -----####
```{r}
ggplot(new_seek, aes(x= reorder(category, -man_woman), y=man_woman, label=man_woman, fill=category)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  scale_fill_discrete("Blues")+
  coord_flip()
```

###------ Loading in gender bias dictonaries -----####
```{r}
gender_dict <- read_csv("Desktop/NLP/scraping/gender_bias_dict.csv")
gender_dict1 <- gender_dict[!(gender_dict$'0'=="-1000"),]

write.csv(gender_dict1, "gender_dict_clean.csv", sep=";")

gender_dict_seek <- read_csv("seek_gender_bias_dict1.csv")
gender_dict_seek1 <- gender_dict_seek[!(gender_dict_seek$'0'=="-1000"),]

```

```{r}
write_csv(new_seek, "DF_SEEK_CLEAN_BIAS.csv")
write_csv(df_bias, "DF_INDEED_CLEAN_BIAS.csv")
```


###------ Adding gender emplyment ratios (value = % of men in sector) -----####
```{r}
indeed_occupation <- df_bias
unique(indeed_occupation$Sector)
indeed_occupation$Ratio[indeed_occupation$Sector == "Construction"] <- 87
indeed_occupation$Ratio[indeed_occupation$Sector == "Professional, Scientific and Technical Services"] <- 57
indeed_occupation$Ratio[indeed_occupation$Sector == "Manufacturing"] <- 72
indeed_occupation$Ratio[indeed_occupation$Sector == "Retail Trade"] <- 55
indeed_occupation$Ratio[indeed_occupation$Sector == "Transport, Postal and Warehousing"] <- 80
indeed_occupation$Ratio[indeed_occupation$Sector == "Accommodation & Food Services"] <- 46
indeed_occupation$Ratio[indeed_occupation$Sector == "Healthcare & Social Assistance"] <- 22
indeed_occupation$Ratio[indeed_occupation$Sector == "Education & Training"] <- 28
indeed_occupation$Ratio[indeed_occupation$Sector == "Creative Arts & Design"] <- 50
indeed_occupation$Ratio[indeed_occupation$Sector == "Business, Consulting & Management"] <- 61
```


###------ Merging subsets of Ratio, Bias and Salary to compare -----####
```{r}
salay_merge <- df_salary
sal_na <- na.omit(salay_merge)
table <- sal_na %>% 
  group_by(Occupation) %>%
  summarise(avg_salary = mean(salary_mean), na.rm = TRUE)

table_bias <- df_bias %>% 
  group_by(Occupation) %>%
  summarise(avg_bias = mean(man_woman), na.rm = TRUE)

table_ratio <- df_bias %>% 
  group_by(Occupation, Sector) %>%
  summarise(avg_ratio = mean(Ratio), na.rm = TRUE)

full_table <- merge(table_ratio, table_bias, by.x="Occupation", by.y = "Occupation", all.x = T)
full_table <- merge(full_table, table, by.x="Occupation", by.y = "Occupation", all.x = T)
full_table <- na.omit(full_table)
```
###------ Plotting Bias against salary  -----####
```{r}
full_table %>% group_by(Occupation) %>% 
  #summarise(mean.gender=mean(man_woman)) %>% 
  ggplot(aes(avg_bias,avg_salary, color=Sector)) + 
  geom_point()+
  geom_text(aes(label=Occupation),hjust=0, vjust=0)+ 
  scale_color_manual(breaks = c("Construction", "Transport, Postal and Warehousing", "Manufacturing", "Professional, Scientific and Technical Services", "Business, Consulting & Management", "Accommodation & Food Services", "Retail Trade", "Creative Arts & Design",  "Education & Training", "Healthcare & Social Assistance"), values=c("blue4", "blue3", "blue2", "blueviolet", "blue1", "cadetblue3", "chocolate", "coral3" ,"coral1" ,"brown1")) + 
  theme_classic()
```
###------ Plotting Bias against Ratio  -----####
```{r}
indeed_occupation %>% group_by(Sector) %>% 
  #summarise(mean.gender=mean(man_woman)) %>% 
  ggplot(aes(mean_bias,Ratio, color=Sector)) + 
  geom_point()+
  geom_smooth(method = "lm")+
  xlim(-0.007, 0.02)+
  ylim(15, 95)+
  geom_text(aes(label=Sector),hjust=0, vjust=0)+ 
  labs(title="Indeed Data: Gender Bias / Gender Ratio - Plot")+
  scale_color_manual(breaks = c("Construction", "Transport, Postal and Warehousing", "Manufacturing", "Professional, Scientific and Technical Services", "Business, Consulting & Management", "Accommodation & Food Services", "Retail Trade", "Creative Arts & Design",  "Education & Training", "Healthcare & Social Assistance"), values=c("blue4", "blue3", "blue2", "blueviolet", "blue1", "cadetblue3", "chocolate", "coral3" ,"coral1" ,"brown1")) + 
  theme_classic()
```
###------ calculating peasons correlation of bias and ratio  -----####
```{r}
cor(df_bias$mean_bias, df_bias$Ratio, method = c("pearson"))
cor.test(df_bias$Ratio, df_bias$mean_bias, method=c("pearson"))
#the mean gender bias is associated with the gender ratio of employment with a Pearson's coefficient P=0.92, p=<.001
```

###------ deviding data into female and male bias + transforming female to absolute values to compare means   -----####
```{r}
#sorry for variable neme, got frustrated 
df_bias$fuck[df_bias$man_woman <= 0] <- "female"
df_bias$fuck[df_bias$man_woman >= 0] <- "male"

df_bias$biases <- "male"
df_bias$biases[df_bias$Sector == "Healthcare & Social Assistance" | df_bias$Sector == "Education & Training"] <- "female"

df_bias$absolute <- abs(df_bias$man_woman)

mean(df_bias$absolute[df_bias$fuck == "female"])
mean(df_bias$absolute[df_bias$fuck == "male"])
sd(df_bias$absolute[df_bias$fuck == "female"])
sd(df_bias$absolute[df_bias$fuck == "male"])

df.summary <- df_bias %>%
  group_by(fuck) %>%
  summarise(
    sd = sd(absolute, na.rm = TRUE),
    len = mean(absolute)
  )
df.summary

ggplot(df.summary, aes(x = fuck, y = len, ymin = len-sd, ymax = len+sd))+
  geom_errorbar(width = 0.2)

t.test(df_bias$absolute[df_bias$fuck == "male"], df_bias$absolute[df_bias$fuck == "female"])
```

#### ----- wordcloud subsets ----- #####
```{r}
subset_male_bias <- subset(df_bias, fuck=="male")
subset_female_bias <- subset(df_bias, fuck=="female")

subset_des_fem <- select(subset_female_bias, Description)
subset_des_male <- select(subset_female_bias, Description)

write_csv(subset_des_fem, "sub_fem.csv")
write_csv(subset_des_male, "sub_man.csv")
```
